% Acknowledgements (optional)

\newpage
\section*{Acknowledgements}
First and foremost, I would like to thank my advisor, Dr. Andy Podgurski for his constant support and guidance.  Dr. Podgurski led me into the field of software testing and reliability and guided me in every project. He is  knowledgable, responsible and patient.  In the first few years of my PhD study, I was stuck on my research project and almost give up. Dr Podgurski shared his innovative ideas with me, and contributed a lot of time to help me overcome the difficulties in the research. Everything would be different without him. 

My sincere thanks also go the members of my committee, Dr. Soumya Ray,  Dr. M. Cenk Cavusoglu and Dr. Xiang Zhang for their invaluable feedback, scientific suggestions and insightful discussions, which helped me improve this dissertation. I would like to give special thanks to Dr. Soumya Ray, who generously offered advices and shared research experiences with me during my Ph.D. study.

I would like to thank all my co-workers at Case Western Reserve University: Dr. Boya Sun, Dr. Gang Shu, Shih-feng Sun, Dr. Mark Renfrew, Feng Cao, Kai Liang,  Erdem Tuna. This work will be impossible without their support and cooperation. I am thankful to my close friends, Jiangli Zhu, Yang Zhang, Jiale Li, Xuefei Wang. 

I deeply appreciate my parents, Xiaomin Wang and Baodong Bai, for their unconditional love and support. My wife, Yang Chen, always encourage me and gives me her best possible support. Thank you, Yang. I couldn’t have done it without you. 

